XXXXX

### 2014-12-18 paper/RDF validation requirements/RDF validation requirements.tex
examples clean up

:CC1 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty foaf:name ;
    owl:allValuesFrom xsd:string ] .
:CC2 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty foaf:givenName ;
    owl:allValuesFrom xsd:string ] .
\end{ex}

@@

\begin{DL}
A $\equiv$ $\forall$ foaf:name . xsd:string \\
B $\equiv$ $\forall$ foaf:givenName . xsd:string \\ 
Human $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
\end{DL}

@@

\begin{ex}
# OWL 2 DL
# --------
:FeelingForce owl:disjointUnionOf ( :CC1 :CC2 ) . 
:CC1 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty :attackingBySword ;
    owl:allValuesFrom xsd:boolean ] .
:CC2 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty :attackingByForce ;
    owl:allValuesFrom xsd:boolean ] .
\end{ex}

@@

\begin{DL}
A $\equiv$ $\forall$ :attackingBySword . xsd:boolean \\
B $\equiv$ $\forall$ :attackingByForce . xsd:boolean \\ 
:FeelingForce $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
\end{DL}

@@

\begin{ex}
# examples
# --------
1. dbo:deathDate before ‘<’ dbo:birthDate
2. dbo:releaseDate after ‘>’ dbo:latestReleaseDate
3. dbo:demolitionDate before ‘<’ dbo:buildingStartDate
\end{ex}

@@

>>>>

:CC1 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty foaf:name ;
    owl:someValuesFrom xsd:string ] .
:CC2 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty foaf:givenName ;
    owl:someValuesFrom xsd:string ] .
\end{ex}

@@

\begin{DL}
A $\equiv$ $\exists$ foaf:name . xsd:string \\
B $\equiv$ $\exists$ foaf:givenName . xsd:string \\ 
Human $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
\end{DL}

@@

\begin{ex}
# OWL 2 DL
# --------
:FeelingForce owl:disjointUnionOf ( :CC1 :CC2 ) . 
:CC1 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty :attackingBySword ;
    owl:someValuesFrom xsd:boolean ] .
:CC2 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty :attackingByForce ;
    owl:someValuesFrom xsd:boolean ] .
\end{ex}

@@

\begin{DL}
A $\equiv$ $\exists$ :attackingBySword . xsd:boolean \\
B $\equiv$ $\exists$ :attackingByForce . xsd:boolean \\ 
:FeelingForce $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
\end{DL}

@@

\begin{itemize}
	\item dbo:deathDate before ‘<’ dbo:birthDate
  \item dbo:releaseDate after ‘>’ dbo:latestReleaseDate
  \item dbo:demolitionDate before ‘<’ dbo:buildingStartDate
\end{itemize}

@@

duplicate strings are not allowed:

\begin{ex}
dc:subject "foo"@en
dc:subject "foo"@fr
dc:subject "bar"@fr
dc:subject "foo"
\end{ex}

There are no identical strings.
